---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# saekernel

<!-- badges: start -->
<!-- badges: end -->

Propose an area-level, non-parametric regression estimator based on Nadaraya-Watson kernel on small area mean. Adopt a two-stage estimation approach proposed by Prasad and Rao (1990). MSE estimators are not readily available, so resampling method that called bootstrap is applied. This package are based on the model proposed in Two stage non-parametric approach for small area estimation by Pushpal Mukhopadhyay and Tapabrata Maiti.

## Installation

You can install the released version of saekernel from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("saekernel")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(saekernel)
## basic example code
```
